The human in the loop: volunteer computing as a socio-technical system

### 2016-02-29 Alife16/paper.tex
Processing new results

%---------------------------------------------------------------
\section{Modeling the performance of a volunteer-based distributed computer} %Cambié el nombre
\label{sec:experiments}

Initial experiments were set up using the OpenShift
PaaS, which provides a free tier within which this 
experiment could be performed. That way, and as required, the hardware
and cloud cost for this experiment were zero. Experiments were
announced through a post in Twitter and other social networks, and
results were published here \citep{DBLP:conf/gecco/GuervosG15}. For the
purpose of this paper, we repeated the announcement several times
through the month of April and then by the beginning of August. All
in all, we have the set of runs with the characteristics shown in
Table \ref{tab:runs}. In general, every experiment took several
days. No particular care was taken about the time of the announcement
or the particular wording. Every {\em experiment} consisted in running
until the solution of the 40-trap problem was found. When the correct
solution was sent to the server, the counter was updated and the pool
of solutions reset to the void set. There was no special intention to wait
until all clients had finished, thus it might happen that, in fact,
the islands running in the browser {\em spill} from one experiment to
the next. However, previous experiments have proven that the influence
of these islands in the next experiment is indeed negligible.
%
\begin{table*}
\caption{Characteristics of the volunteer computing initial runs. \label{tab:runs}}
\begin{center}
\begin{tabular}{l|rr}
\hline
Date & \# experiments & Different IPs \\
\hline
April 4th 4/4 & 57 & 191 \\
April 24th 4/24 &  231 & 559 \\
July 31th 7/31 & 97 & 179 \\
\hline
\end{tabular}
\end{center}
\end{table*}
%
\begin{table*}
\caption{Summary of time per run, number of IPs and number of {\tt
    PUT}s per IP in the initial runs. \label{tab:summary:os}}
\begin{center}
\begin{tabular}{l|ccccccc}
\hline
Date & Median \#IPs & Max \#IPs & Median time (s) & Median \#{\tt
  PUT}s & $<$ 69s & $<$ 3.46s & Inter-exper. correlation\\
\hline
4/4 & 5 & 16 & 2040 & 18 & 14.29\% & 5.36\% & 0.0082 \\
4/24 &  5 & 29 & 732 & 11 & 47.39\% & 3.91\% & 0.0934\\
7/31 & 5 & 14 & 260 & 23 & 27.08\% & 1.04\%  & 0.1741\\
\hline
\end{tabular}
\end{center}
\end{table*}
%
The table shows that every run included more than 50 experiments. The
number of different IPs intervening in them varied from more than one
hundred to more than five hundred in the second experiment.

>>>>

%---------------------------------------------------------------
\section{Modeling the performance of a volunteer-based distributed computer} 
\label{sec:experiments}

Initial experiments were set up using the OpenShift
PaaS, which provides a free tier, making the whole experiment cost
equal to 0. Experiments were
announced through a posts in Twitter and, the latest case, Telegram, and
results were published here \citep{DBLP:conf/gecco/GuervosG15}. For the
purpose of this paper, we repeated the announcement several times
through the month of April and then by the end of February. All
in all, we have the set of runs with the characteristics shown in
Table \ref{tab:runs}. In general, every experiment took several
days. No particular care was taken about the time of the announcement
or the particular wording. Every {\em experiment} consisted in running
until the solution of the 40-trap problem was found. When the correct
solution was sent to the server, the counter was updated and the pool
of solutions reset to the void set. There was no special intention to wait
until all clients had finished, thus it might happen that, in fact,
the islands running in the browser {\em spill} from one experiment to
the next. However, previous experiments have proven that the influence
of these islands in the next experiment is indeed negligible.
%
\begin{table}
\caption{Characteristics of the volunteer computing initial runs. \label{tab:runs}}
\begin{center}
\begin{tabular}{l|rr}
\hline
Date & \# experiments & Different IPs \\
\hline
April 4th 4/4 & 57 & 191 \\
April 24th 4/24 &  231 & 559 \\
July 31th 7/31 & 97 & 179 \\
\hline
\end{tabular}
\end{center}
\end{table}
%
\begin{table*}
\caption{Summary of time per run, number of IPs and number of {\tt
    PUT}s per IP in the initial runs. \label{tab:summary:os}}
\begin{center}
\begin{tabular}{l|ccccccc}
\hline
Date & Median \#IPs & Max \#IPs & Median time (s) & Median \#{\tt
  PUT}s & $<$ 69s & $<$ 3.46s & Inter-exper. correlation\\
\hline
4/4 & 5 & 16 & 2040 & 18 & 14.29\% & 5.36\% & 0.0082 \\
4/24 &  5 & 29 & 732 & 11 & 47.39\% & 3.91\% & 0.0934\\
7/31 & 5 & 14 & 260 & 23 & 27.08\% & 1.04\%  & 0.1741\\
\hline
\end{tabular}
\end{center}
\end{table*}
%
The table shows that every run included more than 50 experiments. The
number of different IPs intervening in them varied from more than one
hundred to more than five hundred in the second experiment.
